---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ">",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

# rtable

`rtable` 

## Installation

You can install the development version from Github.

```r
# install.packages("remotes")
remotes::install_github("JohnCoene/rtable")
```

## How-to

First create an account if you do not have one already. Once logged in, go to your "Account" page and keep note of your API key as we will need it in the next section. Finally visit the [Airtable API documentation page](https://airtable.com/api) and select a base, the documentation will show you the `id` of the base you are viewing. Here we set up the session for the demo "Employee Onboarding" base and its "Onboarding Checklist" table. 

### Setup

Set up your session with the `setup` function. The function will let you pass your `api_key` (__required__), and optionally a `base`, a `table` and a `view`. Here we set up the session for the demo "Employee Onboarding" base, we'll also specify the "All Onboarding Tasks" `view`.

```{r eval=FALSE, echo=TRUE}
library(rtable)
setup(api_key = "xxXXxxxXXx", base = "appfSQILnns4mrSUr", table = "Onboarding Checklist", view = "All Onboarding Tasks")
```

```{r eval=TRUE, echo=FALSE}
library(rtable)
setup(base = "appfSQILnns4mrSUr", table = "Onboarding Checklist", view = "All Onboarding Tasks")
```

Note that you can set up your `api_key` as a global variable by adding the option below to your `.Renviron` or `.Rprofile`.

```r
options("RTABLE_API_KEY" = "xXxxXXXxx")
```

You can check what has been set up with.

```{r}
get_setup()
```

You can always reset the setup with `reset_setup`.

### GET

We can then list records with the `list_records` function. Since we specified a `base`, a `table` and a `view` in our `setup` function we do not need to do so here. If you had not setup the latter previously you can specify them in `list_records`.

```{r}
records <- list_records()
```

We can retrieve a single record with `retrieve_record`.

```{r}
record <- retrieve_record(records[[1]]$id)
```

## Create

We can create a new record with `create_records`

```{r}
df <- data.frame(Name = "It's me")
created <- create_records(df)
```

To demonstrate that it worked we can retrieve it again with `retrieve_record`

```{r}
(rec <- created[[1]]$id) # we'll need it later
retrieve_record(rec)
```

## Update

We can update records with `update_record`. Let's update the one we just created.

```{r}
df <- data.frame(Name = "It's me again!", record_id = rec)
updated <- update_records(df, record_id)
```

We'll retrieve the record we updated and see if it matches the one we updated.

```{r}
updated_record <- retrieve_record(rec)
identical(list(updated_record), updated)
```

## Delete

Finally, we can delete the record we created and updaed.

```{r}
delete_record(rec)
```

Then retrieving the deleted record should error as the record we want to retrieve is inexistent.

```{r, error=TRUE}
retrieve_record(rec)
```