---
title: "RC API"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RC API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document covers the RC (reference class) of rtable.

## Setup

Create your rtable with the `new` method, the method works in a fashion similar to `setup` from the classic API.

Here we set up the session for the demo "Employee Onboarding" base and its "Onboarding Checklist" table. Note that by default the initialisation pulls the records from the table with `list_records`. This can be turned off by setting the `list_records` to `FALSE` when initialising the object, as we demonstrate below.

```r
library(rtable)

rt <- rtable$new(base = "appfSQILnns4mrSUr", table = "Onboarding Checklist", api_key = "xxXXxxxXXX", list_records = FALSE)
```

```{r, eval=TRUE, echo=FALSE}
library(rtable)

rt <- rtable$new(base = "appfSQILnns4mrSUr", table = "Onboarding Checklist", list_records = FALSE)
rt
```

The `rtable` object therefore does not include any record.

```{r}
rt$list_records()
```

This is particularly useful if you want to pass specific parameters to `list_records` and do not want the whole table returned.

## Get

If you want to extract the records you can do so with.

```{r}
rt$get_listed() %>% 
  dplyr::glimpse()
```

## Create

```{r}
new_records <- dplyr::tibble(Name = c("Something", "Some other thing"))
rt$create_records(new_records)
```

You can then fetch the created records with.

```{r}
(created <- rt$get_created())
```

## Update

Now we can update the records we created.

```{r}
update_records <- dplyr::tibble(
  record_id = created$record_id, 
  Name = c("New Name", "Another new name")
)
rt$update_records(update_records, record_id)
```

We can then return the updated records with.

```{r}
(updated <- rt$get_updated())
```

__Important__ Note that at this point the records we initally pulled using the `list_records` method have not been updated, only the remote Airtable was. We can can do so with.

```{r}
rt$refresh()
```

We see that it pulled 20 records as opposed to the 18 previously fetched because we created two new records.

```{r}
rt$get_listed() %>% 
  nrow()
```

## Delete

Finally, we can delete those two records we created and updated.

```{r}
rt$delete_records(created, record_id)
```